\Title

### 2020-12-10 manuscript/manuscript.tex
Add note that the comparison might better for discussion
Divide the section in horizontal and depth
Reviewed the horizontal location part. Mostly some wording changes and
made some lists in the text into bullet points for easier reading.

\documentclass[twocolumn]{article}
\usepackage[left=0.7in,right=0.7in,top=1in,bottom=1in]{geometry}
\setlength{\columnsep}{2\columnsep}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[longend,linesnumbered]{algorithm2e}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage[round,authoryear,sort]{natbib}
\usepackage{url}
\usepackage[pdftex,colorlinks=true]{hyperref}
\usepackage{fancyhdr}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{setspace}

@@

Many variants of the equivalent source technique have been proposed, often
attempting to obtain faster or more accurate solutions.
The key factors that vary between them are: (i) the type of source, (ii)
the location of the sources, and (iii) the solution strategy.
The type of source is most commonly a point mass for gravity or dipole for
magnetics \citep[e.g.,~][]{vonfrese1981, silva1986, mendonca1994, siqueira2017}.
However, right-rectangular prisms \citep[e.g.,][]{barnes2011, jirigalatu2019,
li2020} and tesseroids \citep{bouman2016} have also been used successfully.
In fact, even point sources with a simple inverse distance function, instead of
actual gravity or magnetic fields, can be used as
equivalent sources \citep{cordell1992}.
The sources are often distributed on a regular grid at a constant depth
\citep[e.g.,~][]{leao1989, barnes2011, oliveira2013}
or placed beneath each data point \citep[e.g.,~][]{cordell1992, siqueira2017}.
The model is usually estimated through damped least-squares, which imposes a
heavy computational load when the number of data points is large (e.g.,
airborne and satellite surveys).
To reduce the computational load, \citet{mendonca1994} built the solution
iteratively by incorporating one data point at a time using the ``equivalent
data concept''.
\citet{leao1989} processed the input data using a moving window, only fitting the
data inside the window and predicting observations at the center of the window.
\citet{li2010} and \citet{barnes2011} apply different operations to generate a
sparse representation of the sensitive matrix (respectively, wavelet
compression and quadtree discretization), which significantly improves the
speed of the least-squares solution.
\citet{oliveira2013} parametrized the equivalent layer as a piecewise bivariate
polynomial function, reducing the number of parameters in the solution.
\citet{siqueira2017} developed an iterative solution in which the sensitivity
matrix is transformed into a diagonal matrix with constant terms through the
``excess mass criterion''.
\citet{jirigalatu2019} applied the Gauss-FFT method to speed up the forward
modelling operations and solved the least-squares problem using steepest
descent to avoid calculating the Hessian matrix and solving linear systems.

Many of the existing methods solve under-determined problems, requiring a much
larger number of equivalent sources than the number of data points.
Some achieve greater efficiency by restricting their applications
specific data types \citep{siqueira2017},
interpolating only on regular grids \citep{leao1989},
or requiring already gridded data (CITE PINGA NEW PAPER),
to name a few.
Furthermore, many of the optimizations proposed are also complex to implement
in a computer program, limiting their wider adoption.

In the present study,
we propose a two strategies for reducing the computational load of
the equivalent sources technique:

\begin{enumerate}
    \item Reduce the number of equivalent sources for oversampled surveys
      through a \emph{block-averaging} strategy while maintaining the quality
      of the solution.
    \item Fit the equivalent source model iteratively along overlapping windows
      using a \emph{gradient boosting} algorithm \citep{friedman2001}.
\end{enumerate}

The first strategy consists in dividing the survey area into horizontal blocks
and assign one source to each block, located at the median horizontal location
of the data points. For airborne, shipborne, and satellite surveys, which are
oversampled along tracks, this can greatly reduce the size of the inverse
problem while retaining the same quality of interpolation.

The gradient boosting algorithm allows us to fit the equivalent source model
iteratively by operating on individual overlapping windows.
Thus, our method solves several much smaller least-squares problems instead of
a large one.
This has some similarities with the strategy used by \citet{leao1989} but
without the requirement for sources and predictions to be on regular grids.

Through tests on synthetic data, we show that: (i) the \emph{block-averaged}
sources are able to achieve the same accuracy as other traditional equivalent
source layouts while using a fraction of the number of sources, and (ii) the
\emph{gradient boosting} algorithm greatly reduces the computational memory
required to fit very large datasets without sacrificing prediction accuracy.
Finally, a combination of both strategies are used to process a collection of
around 1.7 million ground gravity data measurements from Australia.

@@

\subsection{Gradient boosting}

Gradient boosting was first introduced by \citet{friedman2001, friedman2002} as
a method for fitting additive parametric models of the form

\begin{equation}
  d = \sum_{k=1}^K \alpha_k f(\mathbf{c}_k),
\end{equation}

\noindent where $\alpha_k$ is a scalar coefficient called the \emph{step-size}
and $f$ is a function of the parameter vector $\mathbf{c}_k$.
For linear regression problems, these additive models can be written as the
matrix equation

\begin{equation}
    \mathbf{d} = \sum_{k=1}^K \alpha_k \mathbf{A}_k \mathbf{c}_k \ .
    \label{eq:gb-linear-model}
\end{equation}

We can transform our equivalent source problem in
equation~\ref{eq:linear-problem} into an additive model by
(1) defining a set of $K$ overlapping windows of equal size that cover the
survey area and (2) defining separate sets of equivalent sources, one per
window. Then, the coefficients $\mathbf{c}_k$ relate to the equivalent sources
of the $k$-th window and $\mathbf{A}_k$ is the Jacobian matrix between
those sources and every data point.
Thus, the predicted data are a superposition of the
effects of the $K$ sets of equivalent sources.

The gradient boosting algorithm above works by fitting each component of the
additive model, one at a time, to the residuals of the previous component.
\citet{friedman2001} demonstrates that this corresponds to a steepest-descent
optimization in the so-called ``function space'', with $\alpha_k$ corresponding
to step sizes in steepest descent.
We can modify the gradient boosting algorithm of \citet{friedman2001} to
find the damped least-squares solutions for the $K$ parameters vectors
$\mathbf{c}_k$ and step sizes $\alpha_k$ in equation~\ref{eq:gb-linear-model}:

\begin{algorithm}[!h]
  \DontPrintSemicolon
  \setstretch{1.5}
  define the residual vector: $\mathbf{r}_{0} = \mathbf{d}^o$ \;
  \For{ $k = 1$ \KwTo $K$ }{

    \nllabel{alg:scale}
    $\mathbf{B}_k = \mathbf{A}_k \mathbf{S}_k\inv$ \;

    \nllabel{alg:fit}
    $
     \hat{\mathbf{m}}_k = \left[\mathbf{B}_k\trans \mathbf{W}_k \mathbf{B}_k +
     \lambda \mathbf{I} \right]\inv \mathbf{B}_k\trans \mathbf{W}_k
     \mathbf{r}_{k-1}
    $ \;

    \nllabel{alg:unscale}
    $\hat{\mathbf{c}}_k = \mathbf{S}_k\inv \hat{\mathbf{m}}_k$ \;

    \nllabel{alg:stepsize}
    $
      \alpha_k = \underset{\alpha}{\mathrm{argmin}}
      \left(
        \left\lVert
          \mathbf{r}_{k - 1} - \alpha \mathbf{A}_k \hat{\mathbf{c}}_k
        \right\rVert ^ 2
      \right)
    $ \;

    \nllabel{alg:residual}
    $\mathbf{r}_k = \mathbf{r}_{k - 1} - \alpha_k\mathbf{A}_k \hat{\mathbf{c}}_k$ \;
  }
  \BlankLine
  \setstretch{1}
  \caption{Gradient boosting solution for damped least-squares regression.}
\end{algorithm}

\citet{friedman2002} suggests that introducing randomness into the fitting
process can improve convergence of the solution. To achieve this, we randomize
the order in which the $K$ windows are used in the gradient boosting algorithm.

The $\mathbf{A}_k$ matrices have only $N \times M_k$ elements, which can be
considerably smaller than the $N \times M$ elements of $\mathbf{A}$.
Therefore, the gradient boosting method allows us to fit
equivalent sources models that would produce Jacobian matrices that are larger
than the available computer memory.
Furthermore, we can increase or decrease the size of the overlapping windows as
needed depending on the number of sources in the model and the available
computer memory.

We can improve the efficiency of the algorithm further by using only data
points that fall within the $k$-th window for fitting the sources
(steps \ref{alg:scale} and \ref{alg:fit}),
while using all available data when calculating the step size and residuals
(steps \ref{alg:stepsize} and \ref{alg:residual}).
By doing so, we reduce the Jacobian matrix further to $N_k \times M_k$
elements.
The forward modeling operations performed in steps \ref{alg:stepsize} and
\ref{alg:residual} can be done by a summation
(TODO: ADD EQUATION)
instead of a matrix-vector product, which allows us to avoid storing the larger
$N \times M_k$ Jacobian.
The influence of distance sources on the solution is maintained by using the
entire set of data points when updating the residuals vector.

The step size parameter functions as scaling factor that prevents the algorithm
from worsening the fit to data points outside of the current window.
As such, it improves the converge of the solution and ensures that the
overall misfit decreases with iteration.
The step size that minimizes the misfit function in step \ref{alg:stepsize} of
the algorithm is

\begin{equation}
    \alpha_k = \frac{
      \mathbf{r}_{k-1}\trans \mathbf{A}_k \hat{\mathbf{c}}_k
    }{
      \hat{\mathbf{c}}_k\trans\mathbf{A}_k\trans \mathbf{A}_k \hat{\mathbf{c}}_k
    }.
\end{equation}

After all $\alpha_k$ step sizes and $\hat{\mathbf{c}}_k$ coefficients vectors
are estimated, we can predict the effect of the additive equivalent source
model on any point through the summation

\begin{equation}
    d(\mathbf{p}) =
    \sum\limits_{k=1}^K \sum\limits_{j=1}^{M_k}
    \alpha_k \frac{{c_k}_j}{\left\lVert \mathbf{p} - \mathbf{q}_j \right\rVert}
    \ .
\end{equation}

SOMETHING ABOUT THE VON FRESE 88 PAPER (BOOTSTRAP INVERSION) AND HOW THIS IS
DIFFERENT.

\subsection{Source distributions}

How to choose how many sources to use and where to locate them are not
trivial decisions that play an important role on the accuracy of the
predictions and the computational resources needed to fit the sources'
coefficients.

The chosen distribution of sources should simultaneously reproduce the measured
data on the survey points and be able to make accurate predictions of the
measured harmonic field on non observed locations.

A high number of sources homogeneously distributed on the survey region are
capable of reproducing the observed data. Nevertheless, too many sources will
make the Jacobian matrix too large, what could introduce computational problems
like the inability of storing the matrix on memory or a high computational time
needed to fit the sources' coefficients.
On the other hand, using very few sources will undoubtedly reduce the memory
needs and lower the computational time when fitting the sources' coefficients.
Nevertheless, it could be incapable of making accurate predictions or even
reproducing the measured data if the number of sources is too low.

The choice of the source distribution could also depend on the characteristic
of the survey and how the observation points are distributed on the region.
A ground survey usually consists in observation points located along irregular
paths plus some possible scattered points.
The survey region is usually heterogeneously covered, leaving areas without any
observation.
On the other hand, an airborne survey consists in observation points located
along almost straight flight lines. The measurements are usually taken at
a high frequency, so the observation points along the flight lines are very
close to each other.
This creates an anisotropy on the observation points: there are much more
observation points along the flight lines directions.

The most widely used source distributions are: a regular grid of point sources
and one point source beneath each observation point.

The \emph{regular grid} creates an homogeneous distribution of point sources
below the surveyed region.
The distance between sources is controlled by the grid spacing parameter.
Keeping the boundaries of the grid constant, reducing the spacing increases the
number of sources.

The \emph{source below data} layout locates one source below each
observation point, therefore the number of sources will be equal to the number
of data points.

When working with ground surveys, the \emph{regular grid} needs the grid
spacing to be sufficiently small so observed values can be accurately
reproduced by the source distribution.
This will create too many sources on areas where no observation has been
carried out.
In contrast, the \emph{source below data} layout is more likely to accurately
fit the observed data with much less sources, reducing the computational load
to fit the equivalent sources' coefficients.

When working with airborne surveys, the \emph{source below data} may
generate an anisotropic distribution of sources by locating too many sources
along the flight paths.
It could lead to unwanted aliases on the predicted values.
In contrast, the \emph{regular grid} won't generate aliases by homogeneously
locating sources.

We propose a new source distribution that could simultaneously reduce the
computational load and remove the drawbacks of the preceding ones: the
\emph{block averaged sources}.
It consist in:

\begin{enumerate}
    \item Dividing the region in blocks of equal size. The size of the blocks
        is controlled by a \emph{spacing} parameter.
        (see Fig.~\ref{fig:block-averaged-sources}(a)-(b)).
    \item Computing the median location of the observation points that fall
        inside each block. Blocks without any observation point are ignored.
    \item Locating one point source below each block averaged coordinate.
        (see Fig.~\ref{fig:block-averaged-sources}(c)).
\end{enumerate}

The number of sources created by this new distribution will be less or equal to
the ones created by the \emph{source below data} and the \emph{regular
grid} with the same spacing.
Moreover, the sources are only located beneath populated blocks, so sources
will be concentrated on regions where data has been gathered and no anisotropic
distribution of sources will be generated.

@@

@@

\begin{table*}
    \centering
    \caption{
        Source distributions as combinations of source layouts and depth
        strategies.
    }
    \label{tab:source-distributions}
    \begin{tabular}{lccc}
        & Source below data & Block averaged sources & Grid sources \\ \hline
        Constant depth & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
        Relative depth & $\checkmark$ & $\checkmark$ & $\times$     \\
        Variable depth & $\checkmark$ & $\checkmark$ & $\times$     \\
    \end{tabular}
\end{table*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\documentclass[twocolumn]{article}
\usepackage[left=0.7in,right=0.7in,top=1in,bottom=1in]{geometry}
\setlength{\columnsep}{2\columnsep}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage[round,authoryear,sort]{natbib}
\usepackage{url}
\usepackage[pdftex,colorlinks=true]{hyperref}
\usepackage{fancyhdr}
\usepackage{multirow}
\usepackage{booktabs}

@@

Many variants of the equivalent source technique have been proposed, often
attempting to obtain faster or more accurate solutions.
The key factors that vary between them are: (i) the type of source, (ii)
the location of the sources, and (iii) the solution strategy.
The type of source is most commonly a point mass for gravity or dipole for
magnetics \citep[e.g.,~][]{vonfrese1981, silva1986, mendonca1994, siqueira2017}.
However, right-rectangular prisms \citep[e.g.,][]{barnes2011, jirigalatu2019,
li2020} and tesseroids \citep{bouman2016} have also been used successfully.
In fact, even point sources with a simple inverse distance function, instead of
actual gravity or magnetic fields, can be used as
equivalent sources \citep{cordell1992}.
The sources are often distributed on a regular grid at a constant depth
\citep[e.g.,~][]{leao1989, barnes2011, oliveira2013}
or placed beneath each data point \citep[e.g.,~][]{cordell1992, siqueira2017}.
The model is usually estimated through damped least-squares, which imposes a
heavy computational load when the number of data points is large (e.g.,
airborne and satellite surveys).
To reduce the computational load, \citet{mendonca1994} built the solution
iteratively by incorporating one data point at a time using the ``equivalent
data concept''.
\citet{leao1989} processed the input data using a moving window, only fitting the
data inside the window and predicting observations at the center of the window.
\citet{li2010} and \citet{barnes2011} apply different operations to generate a
sparse representation of the sensitive matrix (respectively, wavelet
compression and quadtree discretization), which significantly improves the
speed of the least-squares solution.
\citet{oliveira2013} parametrized the equivalent layer as a piecewise bivariate
polynomial function, reducing the number of parameters in the solution.
\citet{siqueira2017} developed an iterative solution in which the sensitivity
matrix is transformed into a diagonal matrix with constant terms through the
``excess mass criterion''.
\citet{jirigalatu2019} applied the Gauss-FFT method to speed up the forward
modelling operations and solved the least-squares problem using steepest
descent to avoid calculating the Hessian matrix and solving linear systems.
Most existing methods solve under-determined problems, requiring a much larger
number of equivalent sources than the number of data points.
Furthermore, many of the optimizations proposed are also complex to implement
in a computer program, limiting their wider adoption.
In the present study,
we propose a two-way method for reducing the computational load needed to apply
the equivalent sources technique: first by reducing the number of equivalent
sources through a \emph{block-averaging} strategy and then simplifying the
fitting process through a \emph{gradient boosting} algorithm.
The first strategy consists in
dividing the survey area into horizontal blocks and assign one source
to each block at the median horizontal location of the data points.
For airborne surveys, which are oversampled along tracks, this can greatly
reduce the size of the inverse problem while retaining the quality of
interpolation.
The second algorithm simplifies the process of fitting a very large number of
equivalent sources by defining sets of fewer sources, whose coefficients are
fitted iteratively while minimizing a given residue.
Through tests on synthetic data, we show that: (i) the \emph{block-averaged}
sources achieve the same accuracy as a traditional equivalent layer while using
a fraction of the number of sources, and (ii) the \emph{gradient boosting}
algorithm greatly reduces the computational memory required to fit very large
datasets without scarifying predictions' accuracy.
Finally these methods are used to interpolate a 1.7 million gravity data
measurements around Australia onto a regular grid.

@@

\subsection{Location of sources}

The ideal number of sources and their locations, both horizontally and
vertically, has been debated since the inception of the equivalent source
technique with \citet{dampney1969}.
The choices made regarding these parameters can play an important role on the
accuracy of the predictions and the computational resources needed to estimate
the coefficients.
An ideal distribution of sources should simultaneously be able to reproduce the
measured data on the survey points and also be able to make accurate
predictions on non-observed locations.

A large number of sources evenly distributed along the survey region are
capable of reproducing the observed data. Nevertheless, the computational load
can be prohibitive and such underdetermined problems are prone to overfiting
the data, leading to poor performance when making predictions. On the other
hand, using very few sources will undoubtedly reduce the computational
requirements but the equivalent source model could be incapable of reproducing
the measured data, leading to inaccurate predictions.

Particular survey characteristics also play a role in the choice of source
distribution.
In a ground survey, observation points are usually located along irregular
paths as well as some possible scattered points.
The coverage of the survey region is usually uneven, often leaving large areas
without any observation.
On the other hand, observations from airborne surveys are located along almost
straight flight lines.
Measurements are usually taken at
a high temporal frequency, leading to the observation points along the flight
lines that are several times closer than the flight line spacing.
This creates an anisotropy in the sampling, which can cause aliasing artifacts
in gridded products.

\subsubsection{Horizontal layout}

The most widely used layouts of equivalent sources are:

\begin{itemize}
  \item
    \emph{Regular grid}: a homogeneous distribution of point sources below the
    survey region at a constant depth. A padding region is often added to help
    reduce edge effect. In practice, often leads to underdetermined problems
    ($N<M$).
  \item
    \emph{Sources below data}: one equivalent source is placed below each
    observation point at a given depth (often dependent on the distance to
    neighboring data points). Therefore, the number of sources is be equal to
    the number of observations ($N=M$).
\end{itemize}

For ground surveys, the \emph{regular-grid} layout needs a sufficiently
small grid spacing to be able to fit the observed data.
This creates an unnecessarily large number of sources in areas where no
observations exist.
In contrast, the \emph{sources-below-data} layout is more likely to accurately
fit the observed data with many fewer sources, reducing the computational load.

For airborne surveys, the \emph{source-below-data} layout may
place an undesirably large number of sources along the flight paths.
This could lead to aliasing effects on the predicted values, such as the
stripes parallel to flight lines that are often observed when griding airborne
magnetic data.
In contrast, the \emph{regular-grid} layout can avoid this effect by evenly
distributing sources and using a continuous source layer (e.g.,
right-rectangular prisms or tesseroids).

We propose a new source layout that could simultaneously reduce the
computational load and remove some of the drawbacks of the regular-grid and
source-below-data layouts:

\begin{itemize}
  \item
    \emph{Block-averaged sources}: point sources are placed in the average
    position of data points that fall within specified spatial blocks
    (Fig.~\ref{fig:block-averaged-sources}). In
    short, this is done by:
    \begin{enumerate}
        \item Dividing the survey region in blocks of equal size
            (Fig.~\ref{fig:block-averaged-sources}a-b).
        \item Computing the median position of the observation points that fall
          inside each block. Blocks without any observation point are ignored.
        \item Assign one point source to the computed median position, shifted
          to a specified depth (Fig.~\ref{fig:block-averaged-sources}c).
    \end{enumerate}
\end{itemize}

The number of sources created by this new layout will be less than or equal to
(if the blocks contain a single data point)
the number of observations.
The overdetermined problems that arise from this layout have a lower
computational load and are less prone to overfiting since the complexity of the
model is lower.
Moreover, the block averaging process can balance the spacing between sources
along a flight line and between adjacent lines.

@@

\subsubsection{Depth of sources}

@@

\begin{table*}
    \centering
    \caption{
        Source distributions as combinations of source layouts and depth
        strategies.
    }
    \label{tab:source-distributions}
    \begin{tabular}{lccc}
        & Source below data & Block averaged sources & Grid sources \\ \hline
        Constant depth & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
        Relative depth & $\checkmark$ & $\checkmark$ & $\times$     \\
        Variable depth & $\checkmark$ & $\checkmark$ & $\times$     \\
    \end{tabular}
\end{table*}

\subsection{Gradient boosted equivalent sources}

Reducing the number of sources might help to lower the amount of computer
memory needed to fit their coefficients, although it may be not enough for
a very large set of observation points.
Even if we can greatly reduce the number of sources, having too many data
points would still produce a Jacobian matrix large enough that cannot fit in
memory.
This problem was already faced by other authors
\citep{mendonca1994, leao1989, li2010, barnes2011, oliveira2013, siqueira2017,
jirigalatu2019}.
The iterative method proposed by \citet{siqueira2017} needs equivalent sources
to be located beneath each observation point, so it cannot take advantage of
the block-averaged sources.
\citet{leao1989} perform the fitting simultaneously with the prediction, what
prevents us to use already fitted equivalent sources to make future
predictions. Besides the method is limited to interpolations on regular grids.
% Add more discussion on why we won't apply any of the following methods
\citet{mendonca1994}
\citet{li2010}
\citet{barnes2011}
\citet{jirigalatu2019}

Here we propose an iterative algorithm for fitting the source coefficients
using a gradient boosting \citep{friedman2001, friedman2002} strategy:
(i) define a collection of overlapping windows of equal size that cover the
survey area,
(ii) define one set of equivalent sources per window,
(iii) iteratively fit the coefficients of each set of sources.
Once every set of sources is fitted, we can predict the value of the field on
any observation point as the effect of every set of equivalent sources.

Lets assume we have $N$ measurements of a harmonic field on observations points
$\{\mathbf{p}_i\}_{i=1}^{N}$ stored in the vector $\mathbf{d} = (d_1, d_2,
\ldots, d_N)^T$. We have defined a set of $M$ point sources located on
$\{\mathbf{q}_j\}_{j=1}^{M}$. Instead of trying to fit the entire set of
coefficients $\mathbf{c}$ at once, we can reduce the problem to fitting $K$
different sets of equivalent sources: we define $K$ overlapping windows of
equal size that cover the whole observation area, and then we create one set of
equivalent sources per window formed by the $\{\mathbf{q}_m\}_{m=1}^{M_k}$
sources that fall inside the $k$-th window.
The observed data should be equal to the superposition of the
effect of every set of equivalent sources:

\begin{equation}
    \mathbf{d} = \sum_{k=1}^K \alpha_k \mathbf{A}_k \mathbf{c}_k,
\end{equation}

\noindent where $\mathbf{c}_k$ is the vector of coefficients for the $k$-th
set of equivalent sources; $\mathbf{A}_k$ is the Jacobian matrix between
those sources and every data point; and each $\alpha_k$ is a constant called
\emph{step-size parameter}.

By applying gradient boosting we can fit each $\mathbf{c}_k$ vector
iteratively: on each iteration a residue vector $\mathbf{r}_k$ (initialized
with the observed data) is used to fit the $\mathbf{c}_k$
coefficients and $\alpha_k$ step-size parameter, and then updated by removing
the effect of the same sources, as follows:

\begin{equation}
    \mathbf{r}_0 = \mathbf{d},
\end{equation}

\begin{equation}
    \mathbf{r}_k = \mathbf{r}_{k-1} - \alpha_k \mathbf{A}_k\mathbf{c}_k.
    \label{eq:residue}
\end{equation}

\noindent On each iteration the $\mathbf{c}_k$ vector and the $\alpha_k$
parameter can be fitted so they minimize the misfit function:

\begin{equation}
    \phi(\mathbf{c}_k) =
        \left\lVert
            \mathbf{r}_{k-1} - \alpha_k \mathbf{A}_k\mathbf{c}_k
        \right\rVert ^ 2
        + \lambda_d \left\lVert \mathbf{c}_k \right\rVert ^2,
\end{equation}

\noindent following the same method described on Section
\ref{sec:eql-inversion}.
Because the $\mathbf{A}_k$ matrices have only $N \times M_k$ elements,
adjusting the size of the overlapping windows can help in reducing the computer
memory needed to fit the source coefficients.
Nevertheless, in case we have too many data points that make the $\mathbf{A}_k$
matrices large enough that they cannot be stored in memory, we can apply one
more simplification on the fitting process: ignore the effect of the $k$-th
sources on any observation point that falls outside the $k$-th window.

Assuming that there are $N_k$ observation points that fall under the $k$-th
window, we can fit the $\mathbf{c}_k$ coefficients by minimizing the following
misfit function:

\begin{equation}
    \phi(\mathbf{c}_k) =
        \left\lVert
            \tilde{\mathbf{r}}_{k-1} - \tilde{\mathbf{A}}_k\mathbf{c}_k
        \right\rVert ^ 2
        + \lambda_d \left\lVert \mathbf{c}_k \right\rVert ^2,
\end{equation}

\noindent where $\tilde{\mathbf{r}}_{k-1}$ is the residue vector containing
only the elements that correspond to the $\{\mathbf{p}_n\}_{n=1}^{N_k}$
observation points that fall under the $k$-th window; and
$\tilde{\mathbf{A}}_k$ is the Jacobian matrix between these observation points
and the $k$-th sources.
Because the $\tilde{\mathbf{A}}_k$ matrices will have $N_k \times M_k$
elements, the computer memory needed for fitting the $\mathbf{c}_k$
coefficients is greatly reduced.

Once the $\mathbf{c}_k$ coefficients are fitted following the same method
described on Section \ref{sec:eql-inversion}, we need to obtain the value
of the step-size parameter $\alpha_k$.
This can be achieved by minimizing the norm of the difference between the
previous residue $\mathbf{r}_{k-1}$ and the effect of the $k$-th sources on
every observation point:

\begin{equation}
    \alpha_k = \underset{\alpha}{\mathrm{argmin}}
    \left(
        \left\lVert
            \mathbf{r}_{k-1} - \alpha \mathbf{A}_k \mathbf{c}_k
        \right\rVert ^ 2
    \right),
\end{equation}

\noindent which leads to:

\begin{equation}
    \alpha_k = \frac{
        \mathbf{r}_{k-1}^T \mathbf{A}_k \mathbf{c}_k
    }{
        \left(\mathbf{A}_k \mathbf{c}_k\right)^T \mathbf{A}_k \mathbf{c}_k
    }.
\end{equation}

This step will improve the convergence of the iterative algorithm and also will
introduce at some extent the effect of the $k$-th sources on every data point,
which was neglected on the fitting of the $\mathbf{c}_k$ coefficients.

Once both the $\alpha_k$ parameter and the $\mathbf{c}_k$ coefficients are
fitted, equation \ref{eq:residue} is applied to update the residue: compute the
effect of the sources belonging to the $k$-th window on every observation
point. Worth noting that when calculating the effect of any number of sources
we don't need to pre-compute the entire Jacobian matrix: we can calculate the
effect of the sources on each observation point by a simple addition of terms,
what means computing each Jacobian element at once when needed.

Because the number of windows is fixed before starting the iteration process,
its number of steps are also fixed to $K$. Moreover, the windows are randomly
shuffled before starting the process to prevent the prioritization of clustered
sets of equivalent sources.

After all $\alpha_k$ parameters and $\mathbf{c}_k$ coefficients vectors are
fitted, we can predict the effect of every equivalent source on any point as
follows:

\begin{equation}
    V(\mathbf{p}) =
    \sum\limits_{k=1}^K \sum\limits_{m=1}^{M_k}
    \frac{\alpha_k {c_k}_m}{|\mathbf{p} - \mathbf{q}_m|}.
\end{equation}
